\chapter*{Abstract}

This thesis explores the nature of aeolian sediment availability and
its influence on aeolian sediment transport. The aim is to improve
large scale and long term aeolian sediment transport estimates in
(nourished) coastal environments. The generally poor performance of
aeolian sediment transport models with respect to measurements in
coastal environments is often accredited to limitations in sediment
availability. Sediment availability can be limited by particular
properties of the bed surface. For example, if the beach is moist or
covered with non-erodible elements, like shells. If sediment
availability is limited, the aeolian sediment transport rate is
governed by the sediment availability rather than the wind transport
capacity.

Aeolian sediment availability is rather intangible as sediment
availability is not only affected by aeolian processes, but also by
marine and meteorological processes that act on a variety of spatial
and temporal scales. The Sand Motor 21 $\mathrm{Mm^3}$ mega
nourishment is used to quantify the spatiotemporal variations in
aeolian sediment availability and its effect on aeolian sediment
transport. The Sand Motor was constructed in 2011 along the Dutch
coast. Aeolian sediment accumulation in the Sand Motor region is low
compared to the wind transport capacity, while the Sand Motor itself
is virtually permanently exposed to wind and accommodates large
fetches. Aeolian sediment availability is therefore likely to dominate
aeolian sediment accumulation.

Multi-annual bi-monthly measurements of the Sand Motor's topography
are used for a large scale aeolian sediment budget analysis. The
analysis revealed that aeolian sediment supply from the dry beach
area, that is almost permanently exposed to wind, diminished a half
year after construction of the Sand Motor. The reduction in aeolian
sediment supply is likely due to the development of a beach armor
layer. In the subsequent years, two-third of the aeolian sediment
deposits originate from the low-lying beaches that are frequently
flooded and therefore often moist.

The importance of the low-lying beaches in the Sand Motor region is
tested during a six-week field campaign. Gradients in aeolian sediment
transport are measured during the field campaign as to localize
aeolian sediment source and sink areas. A consistent supply from the
intertidal beach area was measured that was temporarily deposited at
the higher dry beach. The temporary deposits were transported further
during high water, when sediment supply from the intertidal beach
ceased, resulting in a continuous sediment supply to the dunes. The
temporary deposition of sediment at the dry beach was likely promoted
by the presence of a berm that affects the local wind shear. Moreover,
the berm edge coincided with the onset of the beach armor layer that
might have further promoted deposition of sediment.

The measurements on spatiotemporal variations in aeolian sediment
availability and supply inspired an attempt to capture the
characteristics of aeolian sediment availability in coastal
environments in a comprehensive model approach. The resulting model
simulates spatiotemporal variations in bed surface properties and
their combined influence on aeolian sediment availability and
transport. The implementation of multi-fraction aeolian sediment
transport in the model introduces the recurrence relation between
aeolian sediment availability and transport through self-grading of
sediment.

The model was applied in a four-year hindcast of the Sand Motor mega
nourishment as first field validation. The model reproduces the
multi-annual aeolian sediment erosion and deposition volumes, and the
relative importance of the intertidal beach area as source of aeolian
sediment well. Seasonal variations in aeolian sediment transport are
incidentally missed by the model. The model accuracy is reflected in a
$\mathrm{R^2}$ value of 0.93 when comparing time series of measured
and modeled total aeolian sediment transport volumes in the four years
since construction of the Sand Motor. The results suggest that indeed
significant limitations in sediment availability, due to soil moisture
content and beach armoring, govern aeolian sediment transport in the
Sand Motor region. A comparison with a simulation without limitation
in sediment availability suggests that aeolian sediment availability
in the Sand Motor region is limited to about 25\% of the wind
transport capacity. Moreover, both spatial and temporal variations in
aeolian sediment availability as well as the recurrence relation
between aeolian sediment availability and transport are essential to
accurate long term and large scale aeolian sediment transport
estimates.


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:
