\chapter*{Acknowledgments}
\addchaptertotoc{Acknowledgments}

In the spring of 2012 I was still convinced that I would never engage
in a PhD research as it would be too specialized, too enduring and too
lonely. Four years later, I learned that an enduring (but hardly
lonely) specialization fits me rather well and is an experience I
would not want to have missed. Now I'm indebted to Jaap for bringing
the NEMO proposal to my attention. To Roos for convincing me to apply
for a PhD position after I had been rambling on about the proposal for
weeks, apparently. She was also the one that finally made me accept
that it was time to wrap up and finish. I thank Jaap and Sierd for
their enthusiastic supervision. I thank Marcel for accepting me on the
NEMO project and providing me once again with the freedom to
explore. I thank Deltares for their generous support in this personal
endeavor and Noor and Jolijn for not keeping me up too many nights in
the final year of my research.

I have a special memory towards the six week \textsc{MegaPEX} field
campaign at the Sand Motor, which was a surrealistic experience that
illustrates how a group of overly enthusiastic scientists is able to
built a beautiful scientific dataset from a huge pile of sand. Either
by Meagan's state-of-the-art equipment that apparently require
American-sized \emph{Freedom Poles} for appropriate mounting, or by
the elegance of simple solutions to complex problems, like Nick ``Topo
is My Life'' Cohn walking his daily transects accumulating to the
equivalent of a proper pilgrimage. I will not easily forget the first
time Sierd and I deployed the nails as low-tech measure for
micro-topographic changes over a single tidal cycle. Due to
unfortunate planning we had to measure and retrieve the first batch of
nails (4 cm long, 3 mm thick) in the middle of the night in
pitch-dark. Waving our torches over the beach it took us only about a
few minutes to find a beautiful array of nails protruding proudly
about 1 cm from the bed. Priceless!  We learned so much these weeks. I
thank the entire \textsc{MegaPEX} team for this exhausting experience,
the assistance with our laborious subaerial measurements, the
proliferation of American flags at the Sand Motor (U-S-A!) and the
free pumpkins.

Except for the six weeks at the Sand Motor, I shared a room at the
Faculty of Civil Engineering with my fellow NEMO promovendi Saulo and
Bas, and Max, our adopted son from the NatureCoast project. It has
been a highly fruitful and challenging environment to work in, despite
our research was only superficially related. I much appreciated the
discussions on what we all could do in our newly obtained and
privileged position: the utter necessity of face recognition in our
room, the benefits of having our own 4x4 and the possible improvements
to our typical Dutch bread-and-cheese lunch. But soon we found
ourselves juggling with an enormous amount of actual scientific ideas,
international co-operations, measurement equipment stacked around our
desks and an abundance of data. Scientific research appeared to be a
very practical daily activity. Discussions started to shift
accordingly: how to deploy equipment in the field, how to solder your
own measurement devices, what Python package will get the most out of
your data and when does data analysis become data torture? Finally,
when it occurred to us that the NEMO project had produced more
children than papers, the focus shifted once again to finalizing our
research. I much appreciated the weekly papers \& coffee meetings with
Saulo regarding our writing progress. We both needed it.

As said, these four years appeared not to be so lonely after
all. Luckily, since the best ideas arise in conversation. Little
pieces that fit together and make you understand. I thank
% nemo
Sierd de Vries,
Saulo Meirelles Nunes da Rocha,
Max Radermacher,
Bas Huisman,
Matthieu de Schipper,
Martijn Henriquez,
Ronald Brouwer,
Marcel Stive,
% deltares
Jaap van Thiel de Vries,
Bert van der Valk,
Ad van der Spek,
Arjen Luijendijk,
Dano Roelvink,
Fedor Baart,
Kees den Heijer,
Irv Elshoff,
Mart Borsboom,
% tudelft citg - coastal engineering
Wiepke J{\"a}ger,
Ad Reniers,
% tudelft citg - hydrology
Thom Bogaard,
Martine Rutten,
Susan Steele,
% tudelft ewi
Laurens van der Maaten,
Thea Vuik,
Duncan van der Heul,
% utwente
Lianne van der Weerd,
Kathelijne Wijnberg,
Leonardo Duarte Campos,
Filipe Galiforni Silva,
Isaac Williams,
% utrecht Jasper Brinkkemper, Jantien Rutten,
Gerben Ruessink,
Winnie de Winter,
Pam Hage,
Yvonne Smit,
Jasper Donker,
Timothy Price,
Maarten Kleinhans,
Sebastian Huizer,
Marc Bierkens,
% wageningen
Corjan Nolet,
Joep Keijsers,
Ate Poortinga,
Michel Riksen,
% oregon
Nick Cohn,
Peter Ruggiero,
% north carolina
Laura Moore,
Orencio Dur{\'a}n,
Evan Goldstein,
% uk
Edie Gallagher,
Daniel Buscombe,
Andrew Cooper,
Irene Delgado-Fernandez,
% jgr
Robert Davidson-Arnott,
Tom Barchyn,
Giovanni Coco,
% plymouth
Gerd Masselink,
% megapex
Bonnie Ludka,
Meagan Wengrove,
Caroline Fredriksson,
% overig Rena Hoogland, Quirijn Lodder,
Bas Arens,
Roeland de Zeeuw,
Gideon Maillette de Buy Wenniger,
% students
Tom Janssen,
Rufus Velhorst,
% demo
Leon Roessen,
Bert Bakker,
Jos van Meurs,
Henk Tiggeloven,
Giel Hermans,
Steve van Herk,
Sander de Vree,
Frank Kalkman,
Jaap van Duin
and the anonymous reviewers
for all the little pieces that made up this thesis.

\bigskip

\begin{flushright}
  Bas Hoonhout \\
  Delft, September 2016
\end{flushright}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:

