\documentclass[preprint,12pt,authoryear]{elsarticle}

\usepackage{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{tabularx}
\usepackage{lineno}
\linenumbers*[1]

% add references to research questions in margin
\newcommand{\mrq}[2][]{}
\newcommand{\rrq}[3][]{}
\newboolean{ispaper}
\setboolean{ispaper}{true}

\def\appendixname{}

\journal{Coastal Engineering}

\begin{document}

\begin{frontmatter}

  \title{Aeolian Sediment Supply at a Mega Nourishment}

  \author[tudelft,deltares]{Bas Hoonhout\corref{ca}}
  \ead{b.m.hoonhout@tudelft.nl}
  \ead{bas.hoonhout@deltares.nl}
  \cortext[ca]{Corresponding author}

  \author[tudelft]{Sierd de Vries}

  \address[tudelft]{Delft University of Technology, Faculty of Civil
    Engineering and Geosciences, Department of Hydraulic Engineering,
    Stevinweg 1, 2628CN Delft, The Netherlands.}

  \address[deltares]{Deltares, Department of Hydraulic Engineering,
    Boussinesqweg 1, 2629HV Delft, The Netherlands.}

  \begin{abstract}
    Mega nourishments are intended to enhance growth and resilience of
    coastal dunes on medium to long time scales by stimulation of
    natural sediment transport processes. The growth and resilience of
    coastal dunes largely depends on the presence of a continuous
    supply of aeolian sediment. A recent example of a mega nourishment
    is the 21 $\mathrm{Mm^3}$ mega nourishment known as the Sand
    Motor. The Sand Motor is intended to nourish the entire Holland
    coast over a period of two decades. Four years of bi-monthly
    topographic measurements of the Sand Motor domain provide an
    opportunity to analyze spatiotemporal variations in aeolian
    sediment supply using an aeolian sediment budget analysis. It
    appears that more than 58\% of all aeolian sediment deposits
    originate from the low-lying beaches that are regularly reworked
    by waves. Aeolian sediment supply from higher beaches diminished
    after half a year after construction of the Sand Motor, likely due
    to the formation of deflation lag deposits that constitute a beach
    armor layer. The compartmentalization of the Sand Motor in armored
    and unarmored surfaces suggests that the construction height is an
    important design criterion that influences the lifetime and region
    of influence for any mega nourishment.
  \end{abstract}

  \begin{keyword}
    aeolian sediment transport; aeolian sediment supply; beach
    armoring; sediment budgets; mega nourishment; Sand Motor
  \end{keyword}

\end{frontmatter}

\input{largescale}

\section*{Acknowledgements}
The work discussed in this paper is supported by the ERC-Advanced
Grant 291206 -- Nearshore Monitoring and Modeling (NEMO).

\appendix

\input{appendix_theoreticaltransport}

\section*{References}
\bibliographystyle{apalike} %elsarticle-harv}
\bibliography{bibliography}{}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
