\documentclass[preprint,12pt,authoryear]{elsarticle}

\usepackage{hyperref}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{tabularx}
\usepackage{lineno}
\usepackage{multirow}
\usepackage{longtable}
%\linenumbers*[1]

% add references to research questions in margin
\newcommand{\mrq}[2][]{}
\newcommand{\rrq}[3][]{}
\newboolean{ispaper}
\setboolean{ispaper}{true}

\def\appendixname{}

\journal{Coastal Engineering}

\begin{document}

\begin{frontmatter}

  \title{Simulating Spatiotemporal Aeolian Sediment Supply at a Mega Nourishment}

  \author[deltares]{Bas Hoonhout\corref{ca}}
  \ead{bas.hoonhout@deltares.nl}
  \cortext[ca]{Corresponding author}

  \author[tudelft]{Sierd de Vries}

  \address[deltares]{Deltares, Department of Hydraulic Engineering,
    Boussinesqweg 1, 2629HV Delft, The Netherlands.}

  \address[tudelft]{Delft University of Technology, Faculty of Civil
    Engineering and Geosciences, Department of Hydraulic Engineering,
    Stevinweg 1, 2628CN Delft, The Netherlands.}

  \begin{abstract}
    Mega nourishments are a novel approach to stimulating coastal
    safety and resilience. Mega nourishments are intended to spread
    along the coast on a decadal time scale by natural sediment
    transport processes with a minimum of intrusion into the natural
    coastal system. The supratidal morphodynamic behaviour of mega
    nourishments is not well understood due to complexities introduced
    by limitations in sediment availability to aeolian sediment
    transport. Consequently, the effectiveness of mega nourishments to
    stimulate coastal safety and to influence coastal landscape and
    habitat development remains unknown.

    In this paper we present a detailed 4-year hindcast of the
    morphological development of the Sand Motor mega nourishment in
    The Netherlands. We use the aeolian sediment transport and
    availability model \textsc{AeoLiS} that focuses specifically on
    the simulation of spatiotemporal variations in sediment
    availability. The model includes the recurrence relation between
    sediment availability and aeolian sediment transport through
    self-grading and beach armoring.

    We show that the model is able to reproduce multi-annual aeolian
    sediment transport rates in the Sand Motor domain in the four
    years after its construction. The RMSE is $3 \cdot 10^4 ~
    \mathrm{m^3}$ (7\% of the total sediment accumulation) and
    $\mathrm{R^2}$ is 0.93 when comparing timeseries of total sediment
    accumulation in the dunes, dune lake and lagoon. The combination
    of spatial and temporal variations in aeolian sediment
    availability, due to the combined influence of soil moisture,
    sediment sorting and beach armoring, is essential for an accurate
    estimate of the total sedimentation volume. The simulated feedback
    between aeolian sediment availability and transport is required
    for accurately describing compartmentalization of the beach and
    locating the aeolian sediment source areas in the Sand Motor
    domain.
    
  \end{abstract}

  \begin{keyword}
    aeolian sediment transport; aeolian sediment supply; beach
    armoring; mega nourishment; Sand Motor; numerical model; aeolis
  \end{keyword}

\end{frontmatter}

\input{hindcast_ce}

\section*{Acknowledgements}
The work discussed in this paper is supported by the ERC-Advanced
Grant 291206 -- Nearshore Monitoring and Modeling (NEMO) and Deltares.

\appendix

\input{appendix_modelsettings}

\section*{References}
\bibliographystyle{apalike} %elsarticle-harv}
\bibliography{bibliography}{}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
