\chapter*{Symbols}
\label{ch:symbols}

\begin{longtable}{p{1cm} p{2cm} p{7.75cm}}
  Symbol & Units & Description \\
  \hline
  \endfirsthead
  Symbol & Units & Description \hfill (continued)\\
  \hline
  \endhead
  $\alpha$ & - & Factor to convert from wind velocity to shear velocity. \\
  $\beta$ & - & Ratio between drag coefficients of bare surface and roughness elements. \\
  $\theta_u$ & - & Wind direction. \\
  $\Gamma$ & - & Implicitness parameter. \\
  $\gamma$ & - & Maximum wave height over depth ratio. \\
  $\zeta$ & - & Bed interaction factor. \\
  $\eta$ & m+MSL & Still water level. \\
  $\hat{\eta}$ & m+MSL & Local water level. \\
  $\kappa$ & - & Von K{\'a}rm{\'a}n constant. \\
  $\lambda$ & - & Roughness density. \\
  $\xi$ & - & Surf similarity parameter. \\
  $\rho_{\mathrm{a}}$ & $\mathrm{kg/m^3}$ & Air density. \\
  $\rho_{\mathrm{p}}$ & $\mathrm{kg/m^3}$ & Grain density. \\
  $\rho_{\mathrm{w}}$ & $\mathrm{kg/m^3}$ & Water density. \\
  $\sigma$ & - & Ratio between surface area and frontal area of roughness elements. \\
  $\Phi$ & kg/m/s & Space-integrated entrainment function. \\
  $\phi$ & $\mathrm{kg/m^2/s}$ & Entrainment function. \\
  $\Psi$ & kg/s & Sediment transport potential. \\
  $A$ & - & Empirical coefficient. \\
  $A_{\mathrm{c}}$ & $\mathrm{m^2}$ & Surface area of control area. \\
  $C$ & - & Empirical coefficient to account for grain size distribution width. \\
  $C_{\mathrm{c}}$ & $\mathrm{kg/m^3}$ & Sediment concentration in the air as used by \citet{deVries2014a}. Relates to $c$ as $c = h C_{\mathrm{c}}$. \\
  $c$ & $\mathrm{kg/m^2}$ & Sediment concentration in the air. \\
  $c_{\mathrm{sat}}$ & $\mathrm{kg/m^2}$ & Saturated sediment concentration in the air. \\
  $D$ & $\mathrm{kg/m^2}$ & Total deposition. \\
  $D_{\mathrm{n}}$ & m & Reference median grain size (250 $\mu \mathrm{m}$). \\
  $d$ & m & Water depth. \\
  $d_{50}$ & m & Median grain size. \\
  $d_{\mathrm{n}}$ & m & Nominal grain size. \\
  $E$ & $\mathrm{kg/m^2}$ & Total erosion. \\
  $E_{\mathrm{v}}$ & m/s & Evaporation rate. \\
  $F$ & m & Available fetch. \\
  $\hat{F}$ & m & Effective fetch. \\
  $F_{\mathrm{c}}$ & m & Critical fetch.\\
  $f_{\Delta z_\mathrm{d}}$ & - & Depth of disturbance factor. \\
  $f_{\theta_u}$ & - & Factor to include wind direction in sediment transport capacity. \\
  $f_{u_\mathrm{* th},M}$ & - & Factor to include the influence of moisture to the shear velocity threshold $u_{\mathrm{* th}}$. \\
  $f_{u_\mathrm{* th},R}$ & - & Factor to include the influence of roughness elements to the shear velocity threshold $u_{\mathrm{* th}}$.  Relates to $R_{\mathrm{t}}$ as $R_{\mathrm{t}} = \frac{1}{f_{u_\mathrm{* th},R}}$. \\
  $f_{u_\mathrm{* th},S}$ & - & Factor to include the influence of salt to the shear velocity threshold $u_{\mathrm{* th}}$. \\
  $g$ & $\mathrm{m/s^2}$ & Gravitational constant. \\
  $H$ & m & Offshore wave height. \\
  $\hat{H}$ & m & Local wave height. \\
  $h$ & m & Height of saltation layer. \\
  $i$ & - & Cross-shore grid index. \\
  $j$ & - & Alongshore grid index. \\
  $K^{\mathrm{+}}$ & - & Hydrodynamic addition mask. \\
  $K^{\mathrm{\times}}$ & - & Hydrodynamic multiplication mask. \\
  $k$ & - & Grain size fraction index. \\
  $k_0$ & - & Index of smallest non-erodible grain size fraction. \\
  $l$ & - & Diagonal index. \\
  $m$ & - & Factor to account for difference between mean and maximum shear stress. \\
  $m_{\mathrm{a}}$ & $\mathrm{kg/m^2}$ & Sediment availability. \\
  $n$ & - & Time step index. \\
  $n_{\mathrm{k}}$ & - & Number of grain size fractions. \\
  $n_{\mathrm{pc}}$ & - & Number of counted particles. \\
  $n_{\mathrm{x}}$ & - & Number of grid cells in cross-shore direction. \\
  $n_{\mathrm{y}}$ & - & Number of grid cells in alongshore direction. \\
  $p$ & - & Porosity. \\
  $p_{\mathrm{g}}$ & kg/kg & Geotechnical mass content of water. \\
  $p_{\mathrm{s}}$ & mg/g & Salt content. \\
  $p_{\mathrm{V}}$ & $\mathrm{m^3/m^3}$ & Volumetric water content. \\
  $Q$ & $\mathrm{m^3}$ & Cumulative sediment transport capacity. \\
  $q$ & kg/m/s & Sediment transport rate. \\
  $q_{\mathrm{sat}}$ & kg/m/s & Saturated sediment transport rate. \\
  $R$ & m & Wave runup height. \\
  $R_{\mathrm{t}}$ & - & Ratio between velocity threshold on bare surface $u_{\mathrm{*th,S}}$ and on surface including roughness elements $u_{\mathrm{*th,R}}$. \\
  $S_k$ & - & Degree of saturation of grain size fraction $k$. \\
  $\hat{S}_k$ & - & Effective degree of saturation of grain size fraction $k$, including the bed interaction parameter $\zeta$. \\
  $T$ & s & Adaptation time scale in advection equation. \\
  $t$ & s & Time. \\
  $\Delta t^n$ & s & Size of time step $n$. \\
  $u_*$ & m/s & Shear velocity. \\
  $u_z$ & m/s & Wind velocity at height $z$. \\
  $u_{\mathrm{*th,R}}$ & m/s & Shear velocity threshold of surface including roughness elements. \\
  $u_{\mathrm{*th,S}}$ & m/s & Shear velocity threshold of bare surface. \\
  $u_{\mathrm{*th}}$ & m/s & Shear velocity threshold. \\
  $u_{\mathrm{th}}$ & m/s & Wind velocity threshold. \\
  $u_{z,x}$ & m/s & Wind velocity component in x-direction and at height $z$. \\
  $u_{z,y}$ & m/s & Wind velocity component in y-direction and at height $z$. \\
  $V$ & $\mathrm{m^3}$ & Sediment volume. \\
  $V_{\mathrm{40\%}}$ & $\mathrm{m^3}$ & Sediment volume normalized to 40\% porosity. \\
  $\Delta V^n$ & $\mathrm{m^3}$ & Change in sediment volume in time step $n$. \\
  $w_k$ & - & Weighting factor for grain size fraction $k$ in right-hand-side of the advection equation. \\
  $w_k^{\mathrm{air}}$ & - & Weighting factor for grain size fraction $k$ based on the grain size distribution in the air. \\
  $w_k^{\mathrm{bed}}$ & - & Weighting factor for grain size fraction $k$ based on the grain size distribution in the bed. \\
  $x$ & m & Cross-shore distance. \\
  $\Delta x_{i,j}$ & m & Size of grid cell $i,j$ in cross-shore direction. \\
  $y$ & m & Alongshore distance. \\
  $\Delta y_{i,j}$ & m & Size of grid cell $i,j$ in alongshore direction. \\
  $z$ & m & Height above the bed. \\
  $z'$ & m & Thickness of inner boundary layer. \\
  $z_{\mathrm{b}}$ & m+MSL & Bed level. \\
  $\Delta z_{\mathrm{d}}$ & m & Depth of disturbance. \\
\end{longtable}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:
